---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
source("HBV_var_init_cond.R")
```

Below are the NSE, parameters, and initial conditions from a 500,000 run monte carlo parameterization in the ParameterizeNDC.R file
```{r}
NSE <- 0.70

params <- c(3.019609e+02, 4.028145e+00, 3.223260e-01, 7.908681e-01, 4.296827e-01, 4.072993e+00,
 3.271594e-01, 1.825658e-01, 1.031739e-03, 2.579748e+01, 3.818635e+00, 1)

initcond <- c(0.000000e+00 , 6.883549e+00, 5.937273e+01, 0.000000e+00, 0.000000e+00, 2.778988e+02)
```

Below reads and preps the data, then runs the model using the conditions above
```{r}
#read data
Weather <- read_csv("ArborRelay_Weather_Daily.csv")
NDCQ <- read_csv("NDC_Q_2021_2022_daily.csv")

#join together for model input
inputdatNDC <- inner_join(Weather, NDCQ, by = "datetime")|>
  select(datetime, P = Rainfall_mm_daily, 
         Temp = AirTemp_C_Mean, PET = PET_Tmean_mm_day,
         Qobs = Streamflow_mm_day)

HBVout <- HBV(pars = params, initcond =  initcond, 
              P = inputdatNDC$P,
              Temp = inputdatNDC$Temp,
              PET = inputdatNDC$PET)

#add obs discharge
HBVout <- bind_cols(HBVout, Qobs = inputdatNDC$Qobs, datetime = inputdatNDC$datetime)
```

HBV out columns and what they are
q = discharge
qs = rapid flow (overland, etc)
qi = interflow (upper storage zone)
qb = baseflow (lower storage zone)
Storage = total storage (soil + S1 + S2)
SWE = Snow Water Equivalent
AET = Actual ET
SF = Snowfall
S1 = Upper Zone Storage
S2 = Lower Zone Storage
Soil = Soil Moisture storage
w = water input, precip and snow
P = Precip
PET = PET
Temp = Temp
Qobs = Observed Discharge

```{r}
#plot discharge 
HBVout |>
  ggplot(aes(x = datetime, y = Qobs, color = "Q observed"))+
  geom_line()+
  geom_line(aes(y = q, color = "Q modeled"))+
  theme_classic()+
  ggtitle(paste("NSE =", NSE))
```

```{r}
HBVout |>
  ggplot(aes(x = datetime, y = soil, color = "Soil storage"))+
  geom_line()+
  geom_line(aes(y = S1, color = "Upper Storage"))+
  geom_line(aes(y = S2, color = "Lower Storage"))+
  theme_classic()+
  ggtitle(paste("NSE =", NSE))
```
```{r}
HBVout |>
  ggplot(aes(x = datetime, y = soil))+
  geom_line()+
  ggtitle("Soil Storage")+
  theme_classic()
```
```{r}
HBVout |>
  ggplot(aes(x = datetime, y = S1))+
  geom_line()+
  ggtitle("Upper Storage")+
  theme_classic()
```
```{r}
HBVout |>
  ggplot(aes(x = datetime, y = S2))+
  geom_line()+
  ggtitle("Lower Storage Storage")+
  theme_classic()
```
